---
title: "RStudio Connect User Report - Last `r as.numeric(Sys.getenv('DAYSBACK', 365))` Days"
output:
  html_document:
    css: "styles.css"
editor_options: 
  chunk_output_type: console
---
```{r preflight_check, results='asis', include=TRUE}
if (
  nchar(Sys.getenv("CONNECT_SERVER")) == 0 ||
  nchar(Sys.getenv("CONNECT_API_KEY")) == 0
) {
  print(htmltools::h4("ERROR: Variables Not Defined"))
  print(htmltools::div(
    "The CONNECT_SERVER and CONNECT_API_KEY",
    "environment variables are required in order for this report",
    "to pull usage data.",
    htmltools::br(),
    htmltools::br(),
    "Please define these variables",
    "and then re-run the report.",
    htmltools::br(),
    htmltools::br(),
    style = "max-width: 600px"
  ))
  knitr::knit_exit("Terminating the report early.")
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(reactable)
library(connectapi)

```


This content summary may contain privileged information. The report is generated
using the [RStudio Connect Server API](http://docs.rstudio.com/connect/api) and
the source code is [available online](https://github.com/sol-eng/connect-usage)
if you'd like to customize your analysis. Data is limited to the last `r
days_back` days.

The report uses the environment variables `CONNECT_SERVER` and `CONNECT_API_KEY`
to collect the data. To limit the results to a single publisher, use a publisher
API key.

```{r}
all_users <- get_users(client, page_size = 500)


reactable(all_users,
          resizable = TRUE,
          filterable = TRUE,
          searchable = TRUE,
          striped = TRUE,
          defaultSorted = "active_time"
) 
```

